If we want to make the best possible moves we will have to player model each player, to make the system adapt to their gameplay.
Player modeling is basically when we model a player characteristics and the way they behave throughout the game to gain knowledge about the individual player. 
In poker there are many aspects of the game which could alter the players behaviour, such as position relatively to the dealer, the pot size, active players etc. Therefore it will be crucial to take atleast some of these things into perspective when trying to model a player. One of the reasons why it is necessary to player model every player is because we need to have the opportunity to exploit a weak player. If one keeps making weak moves that we can predict it would be a wise consideration to exploit it.
In a game of poker there will always be good and bad ways of handling a given situation, and this means there will also be an optimal way of handling each players moves. 
The pro players has to be good at adapting to an opponent. Even if the opponent changes their gameplay throughout the game, one must be able to adapt to this, and that is why we need to constantly player model each player.

To player model each player the system has to look at the games previous history while dynamic learning as the game proceeds.
We decided to implement a neural network to achieve our goal of predicting the opponents cards, next move or as a minimum what strength their dealt hand had. This would be done by having the network look at many games played by that specific player.
One of the big advantages of a neural network is that we are able to give a lot of inputs. These inputs will then be weighted by the system in order to come closer to our targeted output.
This will help us cut out all of the noise that occur and leave us with data that is relevant.

