\begin{thebibliography}{100} 
%references
\bibitem {caniwin} caniwin. (no date known) Texas Holdem Heads-Up Preflop Odds [Online]. Available: https://caniwin.com/texasholdem/preflop/heads-up.php
\bibitem {popular} inferisx. (no date known) Top 10 popular card games [Online]. Available: http://topyaps.com/top-10-popular-card-games
\bibitem{Player-Modeling} Marlos C. Machado, Eduardo P. C. Fantini and Luiz Chaimowicz \emph{Player Modeling: What is it? How to do it?}, SBC - Proceedings of SBGames 2011.
\bibitem{opponent-modeling} Aaron Davidson, Darse Billings, Jonathan Schaeffer and Duane Szafron, \emph{Improved Opponent Modeling in Poker},
Department of Computing Science, University of Alberta.
\bibitem{player-agents} Garrett Nicolai and Robert Hilderman, \emph{Algorithms for evolving no-limit Texas Hold'em poker playing agents}, Department of Computer Science, University of Regina, Regina, and Dalhousie University, Halifax, Canada.
\bibitem{neuralnet} Jochen Fröhlich, \emph {Neural Net Components in an Object Oriented Class Structure}, 
ebook pp. 11-28
\bibitem {rules} Poker Listings, \emph {http://www.pokerlistings.com/poker-rules-texas-holdem}


\bibitem {quote} Lily Hay Newman (2015, 01, 14), \emph{Using AI to Study Poker Is Really About Solving Some of the World’s Biggest Problems} line 46-52 [Online]. Available: \url{http://slate.com/blogs/future_tense/2015/01/14/two_player_heads_up_limit_texas_hold_em_poker_weakly_solved_by_ai_researchers}


\bibitem {alberta} University of Alberta Computer Poker Research Group, \emph{http://poker.cs.ualberta.ca/}
\bibitem {neuron} Artificial neuron models, \emph{http://www.willamette.edu/~gorr/classes/cs449/ann-overview.html}
\bibitem {neuroph} Java Neural Network Framework, \emph{http://neuroph.sourceforge.net/}
\bibitem {brain-vs-ai} Brains Vs. Artificial Intelligence, \emph{https://www.cs.cmu.edu/brains-vs-ai}
\end{thebibliography}