\section*{Glossary}

\subsection*{Poker}
\begin{description}
  \item[Texas Hold'em] \hfill \\
  The most popular variance of poker. Game rules \cite{rules}
  \item[Limit / No-limit] \hfill \\
  Restrictions about how much players are allowed to bet or raise. No-limit has no restrictions while in limit you are only allowed to bet and raise a fixed amount.
  \item[Poker game] \hfill \\
  A game is from the players start playing to all except one player have been knocked out or left the game. 
  \item[Poker round] \hfill \\
  A round is from the poker get their hole cards dealt to the winners are found. In each round the players will have new hole cards.
  \item[Game state] \hfill \\
  A poker round is divided into four game states: Pre-flop, flop, turn, river. The difference between the states are the number of community cards dealt. The numbers of community cards dealt are zero, three, four, five for each state respectively. 
  \item[Pre-flop] \hfill \\
  The first game state. Each player is dealt two cards and zero community cards are dealt. After the bidding round the flop will be dealt.
  \item[Flop] \hfill \\
  The second game state. In this state three community cards are dealt. After the bidding round the turn will be dealt.
  \item[Turn] \hfill \\
  The third game state. In this state on community card is dealt making it a total of four community cards. After the bidding round the river will be dealt.
  \item[River] \hfill \\
  The fourth and final game state. In this state on community card is dealt making it a total of five community cards. After the bidding round the winner of the round will be found.
\end{description}



Preflop:
Preflop is the stage before the flop. Each player has been giving 2 cards each.

Flop:
Flop is the stage when the flop cards are on the table (3 cards)

Turn:
Turn is the stage when the turn card is on the table (1 card extra so 4 cards in total)

River: 
River is the stage when the river card is on the table (1 card extra so 5 cards in total)
Game:
A full game is when one of the players has lost and by lost we mean hitting 0 in the bankroll.
Round:
A round is when we have been through all stages, preflop, flop, turn, river and the end of the round when one of the players has won the round by having the best cards.

Hand:
Hand is the 2 two cards a player is holding, therefore reach player has a hand.
Pot:
Pot is the sum of the total amount each player has betted in the given round.
Deck:
Deck is the deck of cards
Bluff:
Bluff is when a player is trying to make the opponent think that he has good cards on his hand by raising or calling when actually he has nothing or very bad cards.
Aggressive:
Aggressive is when a player or computer is playing aggressively
Defensive:
Defensive is when a player or computer is playing aggressively
All-in:
All-in is when a player is betting all of his bankroll
Bankroll:
Bankroll is the total amount that a player has to bet with, when this hits 0 the player has lost the game.
Board:
Board is the table that we are sitting and playing at.
Small blind:
Small blind is an amount that the player who has the small blind HAS to pay even though they want to fold their hand. Small blind is half the amount of big blind.
Big blind:
Big blind is an amount the player who has the small blind HAS to pay even though they want to fold their hand. Big blind is double the amount of small blind.
Check:
Check is when a player doesn’t want to bet but just wants the game to go on.
Call:
Call is when the opponent has betted an amount and if we want to proceed the round we will have to call his bet and lay the same amount into the pot as he did.
Raise:
Raise is when the opponent has betted an amount and if we want to proceed with the round, we can either call his bet or raise the amount by laying more than what our opponent laid into the pot. Thereby our opponent will have to either call, fold or raise.
Fold:
Fold is if you don’t want to play with the cards you have been dealt or the opponents bet is too high for you, given the cards you have on your hand.
Limit:
Limit is so that one playing cannot just bet 100 kr. Or whatever we set the limit to. But perhaps the limit is 10kr for each bet/raise.
No-limit:
No-limit means that a player can bet whatever he wants or raise with whatever amount he has left in his bankroll.
Heads up:
In a heads up we are only having 2 players who play against each other.
