As there are different kinds of poker, there is one which is the most common, which is Texas Hold’em. Therefore this will be the kind of poker this bachelor thesis will be evolving around. This type of poker is also considered to be the type that is the most strategically complex type of the game.
The rules of the game however are fairly simple.
Each player is dealt 2 hole cards, which only the one receive them must be able to see. 
After the players have been dealt their cards, the two players who are sitting next to the dealer must be then ones to lay the blinds.
The players after that can then either fold, call the bet or raise with either big blind or if we are playing no-limit then he can go all the way up to all-in. 
When the first round of betting are finished the dealer will deal 3 community cards which is also known as the flop. These cards are dealt so every player can see what their value is, and then we have another round of betting. When that is done, the dealer will burn a card, which means that that card will not be in play, and then he will draw another and put it face up like the rest of the community cards. This card is known as the turn. The next betting round begins and then the dealer will burn another card and then deal the river card with face up.
Another round of betting, and then finally the players try to make the best hand they can with 5 cards with a combination of their hole cards and the community cards. The player with the best hand will be the winner.
